Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle structure

### 2017-06-12 documents/TriangleScenarioArXiv/ts.tex
removed table of contents and added appropriate reference to Miguel Navascues' recent work

\begin{document}
    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle structure}
    \author{Thomas C. Fraser}
    \email{tcfraser@tcfraser.com}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
    \author{Elie Wolfe}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    % \email{ewolfe@perimeterinstitute.ca}
    \date{\today}
    \begin{abstract}
        It has long been recognized that certain quantum correlations are incompatible with particular assumption about classical causal structure. Given a causal structure of unknown classicality, the presence of such correlations certifies the non-classical nature of the causal structure in a device independent fashion. In the context of two parties sharing a common resource, these non-classical correlations are also known as non-local correlations. Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion. Such criteria were recently were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations? Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary. Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation. We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    \tableofcontents
    % \setlength{\parskip}{1em}

@@

    It is possible to simplify \cref{eq:ww_ineq} by identifying sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3)$ which can be simplified to $P_{ABC}(300)$ by recognizing that $P_{C}(0) + P_{C}(1) + P_{C}(2) + P_{C}(3) = 1$. Upon doing so, one obtains the following,
    \begin{gather*}
        + P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \\
        - P_{ABC}(303)P_{C}(0) - P_{ABC}(313)P_{C}(0) - P_{ABC}(302)P_{C}(1) - P_{AB}(02)P_{C}(2) - \\
        - P_{AB}(03)P_{C}(2) - P_{AB}(20) - P_{AB}(30) - P_{C}(3)P_{C}(0) \leq 0
    \end{gather*}

    In order to understand the importance of \cref{eq:ww_ineq}, there are a couple of important concepts to understand. First, the Fritz distribution was originally known to be incompatible with the Triangle structure due to the perfect correlation between $C$ and the measurement pseudo-settings $A_l, B_l$. The inequality of \cref{eq:ww_ineq} represents a significant advancement in our understanding of non-classicality in the Triangle structure. For example, \cref{eq:ww_ineq} is violated by distributions that do not exhibit perfect correlation between $C$ and $A_l, B_l$. Furthermore, the existence of an inequality capable of witnessing Fritz distribution \textit{is guaranteed}, albeit there was \textit{no guarantee} that the Inflation Technique would be capable of producing such an inequality. In fact, \cref{eq:ww_ineq} was derived using the Wagon-Wheel inflation depicted in \cref{fig:wagon_wheel_inflation}; smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and Cut inflation (\cref{fig:cut_inflation}) are \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution. This result demonstrates that the Inflation Technique is the first tool-set powerful enough to produce causal compatibility inequalities such as \cref{eq:ww_ineq} strong enough to witness incompatible quantum distributions for the Triangle structure. More universally, this result shows that the Inflation Technique is a promising tool for understanding quantum non-classical in more general causal structures.

>>>>

\begin{document}
    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle structure}
    \author{Thomas C. Fraser}
    \email{tcfraser@tcfraser.com}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
    \author{Elie Wolfe}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    % \email{ewolfe@perimeterinstitute.ca}
    \date{\today}
    \begin{abstract}
        It has long been recognized that certain quantum correlations are incompatible with particular assumption about classical causal structure. Given a causal structure of unknown classicality, the presence of such correlations certifies the non-classical nature of the causal structure in a device independent fashion. In the context of two parties sharing a common resource, these non-classical correlations are also known as non-local correlations. Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion. Such criteria were recently were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations? Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary. Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation. We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    % \tableofcontents
    % \setlength{\parskip}{1em}

@@

    It is possible to simplify \cref{eq:ww_ineq} by identifying sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3)$ which can be simplified to $P_{ABC}(300)$ by recognizing that $P_{C}(0) + P_{C}(1) + P_{C}(2) + P_{C}(3) = 1$. Upon doing so, one obtains the following,
    \begin{equation*}
    \begin{gathered}
    \eq\label{eq:ww_ineq_symplified}
        + P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \\
        - P_{ABC}(303)P_{C}(0) - P_{ABC}(313)P_{C}(0) - P_{ABC}(302)P_{C}(1) - P_{AB}(02)P_{C}(2) - \\
        - P_{AB}(03)P_{C}(2) - P_{AB}(20) - P_{AB}(30) - P_{C}(3)P_{C}(0) \leq 0
    \end{gathered}
    \end{equation*}

    In order to understand the importance of \cref{eq:ww_ineq}, there are a couple of important concepts to understand. First, the Fritz distribution was originally known to be incompatible with the Triangle structure due to the perfect correlation between $C$ and the measurement pseudo-settings $A_l, B_l$. The inequality of \cref{eq:ww_ineq} represents a significant advancement in our understanding of non-classicality in the Triangle structure. For example, \cref{eq:ww_ineq} is violated by distributions that do not exhibit perfect correlation between $C$ and $A_l, B_l$. Furthermore, the existence of an inequality capable of witnessing the non-classicality of the Fritz distribution is guaranteed and the Inflation Technique is capable of producing such an inequality~\cite{Navascues_2017}, albeit requiring a sufficiently complex inflation of the Triangle structure. In fact, \cref{eq:ww_ineq} was derived using the Wagon-Wheel inflation depicted in \cref{fig:wagon_wheel_inflation}; smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and others were \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution. This result demonstrates that the Inflation Technique is the first tool-set powerful enough to produce causal compatibility inequalities such as \cref{eq:ww_ineq} strong enough to witness incompatible quantum distributions for the Triangle structure. More universally, this result shows that the Inflation Technique is a promising tool for understanding quantum non-classical in more general causal structures.
